---
title: "Google Trends Analysis: Maternity Harassment Keywords"
author: "Anju Yamada"
format: html
execute:
  echo: true
  warning: false
---


## Data

The dataset was downloaded from **Google Trends** and contains monthly search
interest values (0–100) for the following keywords:

- Matahara (マタハラ)
- Maternity Harassment (マタニティハラスメント)
- Maternity・Harassment (マタニティ・ハラスメント)

Time range: **January 2010 – September 2025**

More details are available in:

- `docs/codebook.md`

---

## Data Preparation

```{r}
library(tidyverse)

# Create output folders
dir.create("output", showWarnings = FALSE, recursive = TRUE)
dir.create("output/figures", showWarnings = FALSE, recursive = TRUE)
dir.create("output/tables", showWarnings = FALSE, recursive = TRUE)

# Load data
path <- file.path("data", "googletrend.csv")
df <- read.csv(path, fileEncoding = "UTF-8-BOM", encoding = "UTF-8")

# Rename columns for clarity
df <- df %>%
  rename(
    `Matahara (マタハラ)` = `マタハラ`,
    `Maternityharassment (マタニティハラスメント)` = `マタニティハラスメント`,
    `Maternity Harassment (マタニティ・ハラスメント)` = `マタニティ.ハラスメント`
  )

# Convert Date column (monthly format)
Sys.setlocale("LC_TIME", "C")
df$Date <- as.Date(paste0(df$Date, "-01"), format = "%y-%b-%d")

# Reshape into long format
df_long <- df %>%
  pivot_longer(
    cols = -Date,
    names_to = "Keyword",
    values_to = "Interest"
  )

# Preview data
head(df_long)
```
## Visualization
```{r}
p <- ggplot(df_long, aes(x = Date, y = Interest, color = Keyword)) +
  geom_line(linewidth = 1) +
  theme_minimal() +
  labs(
    title = "Google Trends Over Time",
    x = "Date",
    y = "Search Interest",
    color = "Keyword"
  )

p
```

## Output
```{r}
# Save figure
png(filename = file.path("output", "figures", "google_trends_over_time.png"),
    width = 1200, height = 720)
print(p)
dev.off()

# Save table
write.csv(df_long,
          file.path("output", "tables", "df_long.csv"),
          row.names = FALSE)

# List outputs (for verification in the report)
list.files("output", recursive = TRUE)
```

## Reproducible pipeline
```bash
bash run.sh
ls -la output
```

## Reproducibility notes
```bash
cat output/session_info.txt
```